\rhead{\xiaowuhao参考文献}
\renewcommand{\refname}{\song\xiaoerhao参考文献}
\begin{thebibliography}{200}
{
\setlength{\itemsep}{-2pt}
%\setlength{\itemindent}{-1em}
{\renewcommand\baselinestretch{1.0}\selectfont
\wuhao
\bibitem{key1}Gao Y, Zhang T, Xiao J. Thematic video thumbnail selection[C]//Image Processing (ICIP), 2009 16th IEEE International Conference on. IEEE, 2009: 4333-4336.
\bibitem{key2}Christel M G. Evaluation and user studies with respect to video summarization and browsing[C]. SPIE, 2006. 
\bibitem{key3}Song Y, Redi M, Vallmitjana J, et al. To Click or Not To Click: Automatic Selection of Beautiful Thumbnails from Videos[C]//Proceedings of the 25th ACM International on Conference on Information and Knowledge Management. ACM, 2016: 659-668.
\bibitem{key4}Nagasaka A, Tanaka Y. Automatic Video Indexing and Full-Video Search for Object Appearances.[C]//Visual Database System Ii, Elsevier. Dallas, United States: ACM, 1991:113C127.
\bibitem{key5}Swain M, Ballard D. Color indexing[J]. International Journal of Computer Vision, 1991,7(1):11C32.
\bibitem{key6}Zhang H, Kankanhalli A, Smoliar S. Automatic partitioning of full-motion video[J]. Multimedia Systems, 1993, 1(1):10C28.
\bibitem{key7}Bouthemy P, Gelgon M, Ganansia F. A unified approach to shot change detection and camera motion characterization[J]. IEEE Transactions on Circuits and Systems for Video Technology,1999, 9(7):1030C1044.
\bibitem{key8}Courtney J. Automatic video indexing via object motion analysis[J]. Pattern Recognition,1997, 30(4):607C625.
\bibitem{key9}Zabih R, Miller J, Mai K. A feature-based algorithm for detecting and classifying production effects[J]. Multimedia systems, 1999, 7(2): 119-128.
\bibitem{key10}Divakaran A, Sun H. Descriptor for spatial distribution of motion activity for compresse dvideo[J]. 2000, 2:392C398.
\bibitem{key11}Yeung M M, Liu B. Efficient matching and clustering of video shots[C]//Image Processing, 1995. Proceedings., International Conference on. IEEE, 1995, 1: 338-341.
\bibitem{key12}Zhang H J, Wu J, Zhong D, et al. An integrated system for content-based video retrieval and browsing[J]. Pattern Recognition, 1997, 30(4):643C658.
\bibitem{key13}董晨晨. 镜头边界检测与关键帧提取技术研究[D]. 南京: 东南大学, 2010.
\bibitem{key14}朱曦, 林行刚. 视频镜头时域分割方法的研究[J]. 计算机学报, 2004, 27(8):1027C1035.
\bibitem{key15}Jeannin S, Jasinschi R, She A, et al. Motion descriptors for content-based video representation[J]. Signal Processing Image Communication, 2000, 16(1-2):59C85.
\bibitem{key16}Ciresan D C, Meier U, Gambardella L M, et al. Convolutional neural network committees for handwritten character classification[C]//Document Analysis and Recognition (ICDAR), 2011 International Conference on. IEEE, 2011: 1135-1139.
\bibitem{key17}Neumann L, Matas J. Scene text localization and recognition with oriented stroke detection[C]//Proceedings of the IEEE International Conference on Computer Vision. Sydney, Australia:IEEE, 2013:97C104.
\bibitem{key18}赵亚琴. 基于内容的视频片段检索技术研究[D]. 南京:南京理工大学, 2007.
\bibitem{key19}冯哲. 基于内容的视频检索中的音频处理[D]. 上海:复旦大学, 2004.
\bibitem{key20}闫乐林. 基于视听信息的视频语义分析与检索技术研究[D]. 北京:北京邮电大学, 2012.
\bibitem{key21}Walker W, Lamere P, Kwok P, et al. Sphinx-4: a flexible open source framework for speech recognition[J]. Sun Microsystems, 2004:1C18.
\bibitem{key22}Hearst M A. TextTiling: Segmenting text into multi-paragraph subtopic passages[J]. Computational linguistics, 1997, 23(1): 33-64.
\bibitem{key23}Hearst M A. Multi-paragraph segmentation of expository text[C]//Proceedings of the 32nd annual meeting on Association for Computational Linguistics. Association for Computational Linguistics, 1994: 9-16.
\bibitem{key24}Banerjee S, Rudnicky A I. A TextTiling based approach to topic boundary detection in meetings[J]. 2006.
\bibitem{key27}Galley M, McKeown K, Fosler-Lussier E, et al. Discourse segmentation of multi-party conversation[C]//Proceedings of the 41st Annual Meeting on Association for Computational Linguistics-Volume 1. Association for Computational Linguistics, 2003: 562-569.
\bibitem{key25}Riedl M, Biemann C. TopicTiling: a text segmentation algorithm based on LDA[C]//Proceedings of ACL 2012 Student Research Workshop. Association for Computational Linguistics, 2012: 37-42.
\bibitem{key26}Blei D M, Ng A Y, Jordan M I. Latent dirichlet allocation[J]. Journal of machine Learning research, 2003, 3(Jan): 993-1022.
\bibitem{key29}Nguyen V A, Boyd-Graber J, Resnik P. SITS: A hierarchical nonparametric model using speaker identity for topic segmentation in multiparty conversations[C]//Proceedings of the 50th Annual Meeting of the Association for Computational Linguistics: Long Papers-Volume 1. Association for Computational Linguistics, 2012: 78-87.
\bibitem{key30}Chen H, Xie L, Feng W, et al. Topic segmentation on spoken documents using self-validated acoustic cuts[J]. Soft Computing, 2015, 19(1): 47-59.
\bibitem{key31}Fragkou P. Text Segmentation using Named Entity Recognition and Co-reference Resolution in English and Greek Texts[J]. arXiv preprint arXiv:1610.09226, 2016.
\bibitem{key32}Choi F Y Y. Advances in domain independent linear text segmentation[C]//Proceedings of the 1st North American chapter of the Association for Computational Linguistics conference. Association for Computational Linguistics, 2000: 26-33.
\bibitem{key33}M. Utiyama and H. Isahara. A statistical model for domain independent text segmentation.In Proceedings of the 9th EACL, pages 491C498, 2001.
\bibitem{key34} R. Kern and M. Granitzer. Efficient linear text segmentation based on information retrieval techniques. In Proceeding of the International Conference on Management of Emergent Digital EcoSystems, 2009.
\bibitem{key35}W. Wolf, “Key frame selection by motion analysis,” in IEEE International
Conference on Acoustics, Speech, and Signal Processing, vol. 2.IEEE, 1996, pp. 1228C1231.
\bibitem{key36}Y.-F. Ma, X.-S. Hua, L. Lu, and H.-J. Zhang, “A generic framework of
user attention model and its application in video summarization,” IEEE Trans. on Multimedia, vol. 7, no. 5, pp. 907C919, 2005.
\bibitem{key37}Y. Cong, J. Yuan, and J. Luo, “Towards scalable summarization of
consumer videos via sparse dictionary selection,” IEEE Trans. on Multimedia, vol. 14, no. 1, pp. 66C75, Feb 2012.
\bibitem{key38}G. Guan, Z. Wang, S. Lu, J. D. Deng, and D. D. Feng, “Keypointbased
keyframe selection,” IEEE Trans. on Circuits and Systems for Video Technology, vol. 23, no. 4, pp. 729C734, 2013.
\bibitem{key39}H.-W. Kang and X.-S. Hua, “To learn representativeness of video
frames,” in ACM International Conference on Multimedia, Singapore, November 2005, pp. 423C426.
\bibitem{key40}Zhang B, Wang Z, Tao D, et al. Automatic Preview Frame Selection for Online Videos[C]//Digital Image Computing: Techniques and Applications (DICTA), 2015 International Conference on. IEEE, 2015: 1-6.
\bibitem{key41}Song Y, Redi M, Vallmitjana J, et al. To Click or Not To Click: Automatic Selection of Beautiful Thumbnails from Videos[C]//Proceedings of the 25th ACM International on Conference on Information and Knowledge Management. ACM, 2016: 659-668.
\bibitem{key42}C. Liu, Q. Huang, and S. Jiang. Query sensitive dynamic
web video thumbnail generation. In ICIP, pages 2449C2452, 2011.
\bibitem{key43}D. Joshi, J. Wang, and J. Li, “The story picturing engine: finding elite images to illustrate a story using mutual reinforcement,” ACM SIGMM workshop on MIR, 2004.
\bibitem{key44}Liu W, Mei T, Zhang Y, et al. Multi-task deep visual-semantic embedding for video thumbnail selection[C]//Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2015: 3707-3715.
\bibitem{key45} Apostolidis E, Mezaris V. Fast shot segmentation combining global and local visual descriptors[C]//Acoustics, Speech and Signal Processing (ICASSP), 2014 IEEE International Conference on. IEEE, 2014: 6583-6587.
\bibitem{key46} Smith R. An overview of the Tesseract OCR engine[C]//Document Analysis and Recognition, 2007. ICDAR 2007. Ninth International Conference on. IEEE, 2007, 2: 629-633.
\bibitem{key47} Smith R, Antonova D, Lee D S. Adapting the Tesseract open source OCR engine for multilingual OCR[C]//Proceedings of the International Workshop on Multilingual OCR. ACM, 2009: 1.
\bibitem{key48} Hassan Z, Mohamad A R, Kalil M R, et al. Evaluation of Microsoft speech recognition in controlling robot soccer[C]//Pattern Analysis and Intelligent Robotics (ICPAIR), 2011 International Conference on. IEEE, 2011, 1: 114-118.
\bibitem{key49} Sultana S, Akhand M A H, Das P K, et al. Bangla speech-to-text conversion using SAPI[C]//Computer and Communication Engineering (ICCCE), 2012 International Conference on. IEEE, 2012: 385-390.
\bibitem{key50} Son J W, Lee S Y, Park S Y, et al. Video scene segmentation based on multiview shot representation[C]//Information and Communication Technology Convergence (ICTC), 2016 International Conference on. IEEE, 2016: 381-383.
\bibitem{key51} Griffiths T L, Steyvers M. Finding scientific topics[J]. Proceedings of the National academy of Sciences, 2004, 101(suppl 1): 5228-5235.
%%\bibitem{citekey1}Jian Zhang, Sharp static analysis of programs, Chinese Journal of Computers, 31 (9), 2008, 1549$\sim$1553
%%\bibitem{}Sylvain Paris, Pierre Kornprobst et al., Bilateral filtering: Theory and   applications. Computer Graphics and Vision, Vol. 4, No. 1, 2008, 1$\sim$73
%%\bibitem{}苏步青，刘鼎元，计算几何，上海，上海科学技术出版社，1981
%%\bibitem{}R. Walker, Algebraic Curves, New York， Springer Verlag, 1978
%%\bibitem{}W. M. Hsu, J. F. Hughes, H. Kaufman, Direct manipulation of free-formdeformation, In Proceedings of ACM SIGGRAPH'92, New York, ACM Press,1992, 177$\sim$184
%%\bibitem{}C. Chen, The Research on Piecewise Algebraic Surface Module, PhD Thesis, China University of Technology, 2000

}
}
\end{thebibliography}



